---
title: "Dissertation Version2"
author: "Shuying Mai"
date: "6/25/2023"
output: html_document
---

```{r}
library(osmdata)
library(curl)
library(tidyverse)
library(sf)
library(ragg)
library(extrafont)
library(rnaturalearth)
library(paletteer)
library(forcats)
library(lwgeom)
library(terra)
library(sp)# classes and functions for raster data
library(spData)        # load geographic data
#library(spDataLarge)   # load larger geographic data
library(tmap)    # for static and interactive maps
library(leaflet) # for interactive maps
library(ggplot2) # tidyverse data visualization package
library(grid)
```

## Data Loading
pub
```{r}
pub<-st_read('amenity_EPSG4326.gpkg', layer="amenity_EPSG4326_point", query="SELECT * FROM \"amenity_EPSG4326_point\" WHERE amenity IN ('pub')")
#pub
```
bar
```{r}
bar<-st_read('amenity_EPSG4326.gpkg', layer="amenity_EPSG4326_point", query="SELECT * FROM \"amenity_EPSG4326_point\" WHERE amenity IN ('bar')")
#bar
```
biergarten
```{r}
bg<-st_read('amenity_EPSG4326.gpkg', layer="amenity_EPSG4326_point", query="SELECT * FROM \"amenity_EPSG4326_point\" WHERE amenity IN ('biergarten')")
#bg
```
nightclub
```{r}
club<-st_read('amenity_EPSG4326.gpkg', layer="amenity_EPSG4326_point", query="SELECT * FROM \"amenity_EPSG4326_point\" WHERE amenity IN ('nightclub')")
#club
```

alcohol
```{r}
ach<-st_read('shop_EPSG4326.gpkg', layer="shop_EPSG4326_point", query="SELECT * FROM \"shop_EPSG4326_point\" WHERE shop IN ('alcohol')")
ach$amenity<-"off-premise"
```
beverages
```{r}
#bvr<-st_read('shop_EPSG4326.gpkg', layer="shop_EPSG4326_point", query="SELECT * FROM \"shop_EPSG4326_point\" WHERE shop IN ('beverages')")
```
LA boundaries
```{r}
la<-st_read('Local_Authority_Districts_December_2022_Boundaries_UK_BFC_-5979566790322312414.gpkg')
#la
```
ward boundaries
```{r}
wards<-st_read('Wards_December_2022_Boundaries_UK_BGC_-8100696825722307821.gpkg')
#wards
```

plot of LA and wards
```{r}
plot(st_geometry(la["LAD22NM"]),lwd=0.1)
```

```{r}
plot(st_geometry(wards["WD22NM"]),lwd=0.1)
```
data in the UK
```{r}
uk = world[world$name_long == "United Kingdom", ]
pubUK<-pub[st_within(pub["_ogr_geometry_"],uk["geom"],sparse = FALSE)[,1],]
barUK<-bar[st_within(bar["_ogr_geometry_"],uk["geom"],sparse = FALSE)[,1],]
bgUK<-bg[st_within(bg["_ogr_geometry_"],uk["geom"],sparse = FALSE)[,1],]
clubUK<-club[st_within(club["_ogr_geometry_"],uk["geom"],sparse = FALSE)[,1],]
achUK<-ach[st_within(ach["_ogr_geometry_"],uk["geom"],sparse = FALSE)[,1],]
#bvrUK<-bvr[st_within(bvr["_ogr_geometry_"],uk["geom"],sparse = FALSE)[,1],]
dataUK<-rbind(pubUK,barUK,bgUK,clubUK,achUK)#,bvrUK)
```

```{r}
uk = world[world$name_long == "United Kingdom", ]
world_europe = world[world$continent == "Europe", ]
plot(st_geometry(uk), col = "gray", lwd = 1)
plot(st_geometry(world_europe), add = TRUE)
plot(st_geometry(wards["WD22NM"]),lwd=0.05, add=TRUE)
plot(dataUK["amenity"],pch=1, add = TRUE)
#plot(dataUK[dataUK$name=="Maguire's Pub",],pch=1, add = TRUE)
```

## counts of shops by LA
```{r}
crs_to_use<-st_crs(la)#(dataUK)
crs_epsg<-crs_to_use$epsg

dataUKcrs<-st_transform(dataUK,crs=crs_epsg)
#lacrs<-st_transform(la,crs=crs_epsg)
# 进行空间连接和计数
joined <- st_join(dataUKcrs,la,join=st_within)
```

```{r}
nul<-joined[is.na(joined$LAD22CD),]
#nul
```


```{r}
tmap_save(Null,"Null.html")
```

manually change
```{r}
#%joined[joined$osm_id==4929046352,]$LAD22NM<-"Fermanagh and Omagh"
#%joined[joined$osm_id==4929046352,]$LAD22CD<-"N09000006"
#%joined[joined$osm_id==3101640528,]$LAD22NM<-"Fermanagh and Omagh"
#%joined[joined$osm_id==3101640528,]$LAD22CD<-"N09000006"
#%joined[joined$osm_id==7460660384,]$LAD22NM<-"Causeway Coast and Glens"
#%joined[joined$osm_id==7460660384,]$LAD22CD<-"N09000004"
#%joined[joined$osm_id==794378101,]$LAD22NM<-"Newry, Mourne and Down"
#%joined[joined$osm_id==794378101,]$LAD22CD<-"N09000010"
#%joined[joined$osm_id==1682179186,]$LAD22NM<-"Newry, Mourne and Down"
#%joined[joined$osm_id==1682179186,]$LAD22CD<-"N09000010"
joined[joined$osm_id==5959999933,]$LAD22NM<-"Portsmouth"
joined[joined$osm_id==5959999933,]$LAD22CD<-"E06000044"
joined[joined$osm_id==1299977723,]$LAD22NM<-"Portsmouth"
joined[joined$osm_id==1299977723,]$LAD22CD<-"E06000044"
joined[joined$osm_id==617437775,]$LAD22NM<-"Ceredigion"
joined[joined$osm_id==617437775,]$LAD22CD<-"E06000008"
joined[joined$osm_id==1527601378,]$LAD22NM<-"Brighton and Hove"
joined[joined$osm_id==1527601378,]$LAD22CD<-"E06000043"

joined[joined$osm_id==9705021317,]$LAD22NM<-"Isle of Wight"
joined[joined$osm_id==9705021317,]$LAD22CD<-"E06000046"
joined[joined$osm_id==5420392183,]$LAD22NM<-"Arun"
joined[joined$osm_id==5420392183,]$LAD22CD<-"E07000224"
joined[joined$osm_id==6800626687,]$LAD22NM<-"Arun"
joined[joined$osm_id==6800626687,]$LAD22CD<-"E07000224"
joined[joined$osm_id==1527704723,]$LAD22NM<-"Brighton and Hove"
joined[joined$osm_id==1527704723,]$LAD22CD<-"E06000043"
joined[joined$osm_id==764901582,]$LAD22NM<-"Brighton and Hove"
joined[joined$osm_id==764901582,]$LAD22CD<-"E06000043"
joined[joined$osm_id==4975270288,]$LAD22NM<-"Wandsworth"
joined[joined$osm_id==4975270288,]$LAD22CD<-"E09000032"
joined[joined$osm_id==4559315025,]$LAD22NM<-"Southwark"
joined[joined$osm_id==4559315025,]$LAD22CD<-"E09000028"
joined[joined$osm_id==7525867150,]$LAD22NM<-"Gravesham"
joined[joined$osm_id==7525867150,]$LAD22CD<-"E07000109"
#%joined[joined$osm_id==1786762185,]$LAD22NM<-"North Norfolk"
#%joined[joined$osm_id==1786762185,]$LAD22CD<-"E07000147"
joined[joined$osm_id==10031479605,]$LAD22NM<-"Gwynedd"
joined[joined$osm_id==10031479605,]$LAD22CD<-"W06000002"
joined[joined$osm_id==1298783012,]$LAD22NM<-"Glasgow City"
joined[joined$osm_id==1298783012,]$LAD22CD<-"S12000049"
joined[joined$osm_id==8192076450,]$LAD22NM<-"Ceredigion"
joined[joined$osm_id==8192076450,]$LAD22CD<-"W06000008"
#Maguire’s Pub Fitzpatrick’s and Victoria's ->point empty ->delete
```

```{r}
joined<-joined[!is.na(joined$LAD22CD),]
```

```{r}
counts <- joined %>%
  group_by(LAD22CD) %>%
  summarise(point_count = n())  # 计算每个地理区域中的点的个数

# 打印结果
print(counts)
```


## population and density at LA level
```{r}
library(readxl)
pop<-read_excel("population2021_LA.xls",
                sheet="MYE2 - Persons",skip=7,col_names = TRUE)
pop
```

```{r}
counts_df<-data.frame(counts)
pop_merged<-merge(counts_df,pop,by.x="LAD22CD",by.y="Code",all=TRUE) 
#outer join, but a lot of NA
```

```{r}
pop_merged$density<-pop_merged$point_count/pop_merged$`All ages`*10000
```
Global environment saved here. (mac.RData)

```{r}
pdf("CountsPerLA.pdf")
hist(engpop$point_count,main="Histogram of Counts per LA in England", xlab="Count per LA")
dev.off()
```
```{r}
tmap_mode("plot")
Countmap = tm_shape(merge(la,counts_df,by="LAD22CD",all=TRUE) ) +tm_polygons(col="point_count",title="Outlets Count per LA") #+ tm_symbols(col="red",size="clusters")
Countmap
```
```{r}
tmap_save(Countmap, "CountPerLA.pdf")
```

```{r}
dendata<-merge(la,pop_merged,by="LAD22CD",all=TRUE)
dendata1<-dendata
dendata1[dendata1$LAD22CD=="E09000001",]$density<-NA
```
```{r}
tmap_mode("plot")
Denmap = tm_shape(dendata1) +tm_polygons(col="density",title="Density per LA") #+ tm_symbols(col="red",size="clusters")
Denmap
```

```{r}
tmap_save(Denmap, "DenPerLA.pdf")
```

```{r}
engpop<-pop_merged[grepl("E", pop_merged$LAD22CD), ]
engpop1<-pop_merged1[grepl("E", pop_merged1$LAD22CD), ]
```

```{r}
pdf("DensityPerLA.pdf")
plot(pop_merged$density,main="Scatter Plot of Density per LA",xlab="Local Authority Index", ylab="Density per LA")
dev.off()
```
```{r}
pdf("DensityPlot.pdf")
den<-density(pop_merged$density,na.rm=TRUE)
plot(den,frame=FALSE,main="Density Plot of Density per LA")
dev.off()
```

## Cluster plot
```{r}
tmap_mode("view")
mapCount = tm_layout(frame = FALSE) + tm_shape(dataUK) + 
  tm_dots(legend.show = TRUE,col="amenity",clustering=T, id="name")
mapCount
```

```{r}
tmap_save(mapCount,"mapCount.html")
```

## dbscan
```{r}
library("dbscan")
```

```{r}
tmap_mode("view")
for (eps in c(50,100,150,200,250,300)) {
  for (minPts in c(2,3,5)) {
    coord<-st_coordinates(joined$`_ogr_geometry_`)
    nn<-frNN(coord,eps) #eps
    test<-dbscan(nn,minPts=minPts) #minPoint
    labels<-test$cluster
    cat(paste("When eps =",eps),"and",paste("minPts =",minPts),", the   number of labels is:")
    print(max(labels))
    testData<-joined
    testData$label<-labels
    testData$layer<-testData$label%%26 
    #26 is the length of paletteer_d("ggsci::default_ucscgb")
    testData$layer<-as.factor(testData$layer)
  
    core<-is.corepoint(coord,eps,minPts=minPts)
    circle<-st_buffer(testData[core,],eps)
    cl_boundary<-circle %>% group_by(label) %>% summarise(`_ogr_geometry_`=st_union(`_ogr_geometry_`),do_union=FALSE)
  
    filename<-paste0("eps_",eps,"_minPts_",minPts,".html")
    labelmap = tm_shape(testData) + tm_dots(legend.show = FALSE, id="label",col="layer",palette=paletteer_d("ggsci::default_ucscgb")) + tm_shape(cl_boundary) +tm_borders() + tmap_options(check.and.fix = TRUE)
    tmap_save(labelmap,filename)
    
    manData<-testData[testData$LAD22NM=="Manchester",]
    # manCluNumIn<-st_within(cl_boundary,la[la$LAD22NM=="Manchester",])
    # manClu<-which(as.vector(as.matrix(manCluNumIn))) 
    Clu<-unique(manData$label)
    Clu<-Clu[Clu!=0]
    #find out the num of cluster contained in Manchester
    filename2<-paste0("eps_",eps,"_minPts_",minPts,".txt")
    con<-file(filename2,"w")
    writeLines(paste("The number of clusters in Manchester with epsilon",eps,"and minimum points", minPts, ":", length(Clu)), con)
    for (cluster in Clu){
      data<-testData[testData$label==cluster,]
      writeLines(paste("cluster number:",cluster),con)
      writeLines(paste(names(table(data$amenity)), table(data$amenity)), con)
    }
    close(con)
    
     # Clean up unnecessary variables after each loop
    rm(coord, nn, test, labels, testData, core, circle, cl_boundary, labelmap, manData, Clu, data, filename, filename2, con)
    gc()  # manually call the garbage collector
  }
}
```


find core points and circle boundaries
```{r}
# core<-is.corepoint(coord,eps,minPts=minPts)
# circle<-st_buffer(testData[core,],eps)
# cl_boundary<-circle %>% group_by(label) %>% summarise(`_ogr_geometry_`=st_union(`_ogr_geometry_`),do_union=FALSE)
```

```{r}
# tm_shape(testData) + tm_dots(legend.show = TRUE, col="label",id="label",palette=paletteer_d("ggsci::default_ucscgb")) + tm_shape(cl_boundary) +tm_borders()+tmap_options(check.and.fix = TRUE)
```

find clusters in manchester using eps=100, minPts=3
```{r}
eps<-100
minPts<-5
coord<-st_coordinates(joined$`_ogr_geometry_`)
nn<-frNN(coord,eps) #eps
test<-dbscan(nn,minPts=minPts) #minPoint
labels<-test$cluster
cat(paste("When eps =",eps),"and",paste("minPts =",minPts),", the   number of labels is:")
print(max(labels))
testData<-joined
testData$label<-labels
testData$layer<-testData$label%%26

core<-is.corepoint(coord,eps,minPts=minPts)
circle<-st_buffer(testData[core,],eps)
cl_boundary<-circle %>% group_by(label) %>% summarise(`_ogr_geometry_`=st_union(`_ogr_geometry_`),do_union=FALSE)
```
```{r}
manData<-testData[testData$LAD22NM=="Manchester",]
manCluNum<-length(unique(manData$label))
manCluNumIn<-st_within(cl_boundary,la[la$LAD22NM=="Manchester",])
print(manCluNum)
sum(unlist(manCluNumIn))
#There will be some clusters in the boundary of the LA.
```
clusters within Manchester
```{r}
# #manData<-testData[testData$LAD22NM=="Manchester",]
# #manCluNumIn<-st_within(cl_boundary,la[la$LAD22NM=="Manchester",])
# manClu<-which(as.vector(as.matrix(manCluNumIn))) 
# #find out the num of cluster contained in Manchester
# con<-file("test.txt","w")
# for (cluster in manClu){
#   data<-manData[manData$label==cluster,]
#   writeLines(paste("cluster number:",cluster),con)
#   writeLines(paste(names(table(data$amenity)), table(data$amenity)), con)
# }
# close(con)

```

clusters intersect
```{r}
#manData<-testData[testData$LAD22NM=="Manchester",]
#manCluNumIn<-st_within(cl_boundary,la[la$LAD22NM=="Manchester",])
Clu<-unique(manData$label)
Clu<-Clu[Clu!=0]
#find out the num of cluster contained in Manchester
con<-file("test.txt","w")
for (cluster in Clu){
  data<-testData[testData$label==cluster,]
  writeLines(paste("cluster number:",cluster),con)
  writeLines(paste(names(table(data$amenity)), table(data$amenity)), con)
}
close(con)
```


convex hull
```{r}
# tmap_mode("view")
# for (eps in c(50,100,150,200,250,300)) {
#   for (minPts in c(2,3,5)) {
#     coord<-st_coordinates(dataUKcrs$`_ogr_geometry_`)
#     nn<-frNN(coord,eps) #eps
#     test<-dbscan(nn,minPts=minPts) #minPoint
#     labels<-test$cluster
#     cat(paste("When eps =",eps),"and",paste("minPts =",minPts),", the number of labels is:")
#     print(max(labels))
#     testData<-dataUK
#     testData$label<-labels
#     
#     Poly<-testData[testData$label!=0,] %>% group_by(label) %>% summarise() %>% st_convex_hull()
#     
#     filename<-paste0("eps_",eps,"_minPts_",minPts,".html")
#     labelmap = tm_shape(testData) + tm_dots(legend.show = TRUE,col="label",id="name") +
#       tm_shape(Poly) + tm_borders() 
#     tmap_save(labelmap,filename)
#   }
# }
```

```{r}
Poly<-testData[testData$label!=0,] %>% group_by(label) %>% summarise() %>% st_convex_hull()
plot(Poly)

```



```{r}
#pdf("clusters.pdf",height=10, width=14)
testData$layer<-as.factor(testData$layer)
#library(RColorBrewer)

#initial_palette <- brewer.pal(9, "Set3")

# 根据你的label数量重复调色板以获得所需长度
#n_labels <- length(unique(testData$label))
#palette_colors <- rep(initial_palette, ceiling(n_labels/9))[1:n_labels]



tmap_mode("view")
labelmap = #tm_shape(st_geometry(uk), col = "gray", lwd = 1,name="UK") + tm_polygons() + 
  #tm_layout(frame = FALSE) + tm_shape(wards["WD22NM"],id="WD22NM",name="Wards") + tm_polygons() +
  #tm_shape(st_geometry(wards["WD22NM"]),lwd=0.05,name="Wards") + tm_polygons(id="WD22NM") + 
  tm_shape(testData) + tm_dots(legend.show = FALSE,col="layer",palette=paletteer_d("ggsci::default_ucscgb"), id="label") + 
#,palette=paletteer_d("ggsci::default_ucscgb")) #+ tm_polygons(poly) 
  tm_shape(Poly) + tm_borders() 
labelmap
#dev.off()
```

```{r}
tmap_mode("plot")
clumap = tm_shape(deplaData1) +tm_polygons(col="clusters",title="Count of Clusters per LA") #+ tm_symbols(col="red",size="clusters")
clumap
```

```{r}
tmap_save(labelmap, "Polygon.html")
```

```{r}
engdepladata<-deplaData[grepl("E", deplaData$LAD22CD), ]
engdepladata1<-deplaData1[grepl("E", deplaData1$LAD22CD), ]
```

```{r}
pdf("EnglandCluster.pdf")
hist(engdepladata1$clusters,main="Histogram of Clusters Counts per LA in England",xlab="Clusters Count")
dev.off
```

```{r}
pdf("ClusterPerLA.pdf")
hist(deplaData1$clusters,main="Histogram of Clusters Counts per LA",xlab="Clusters Count")
dev.off()
```

## Deprivation index
```{r}
lsoa<-st_read('LSOA_Dec_2021_Boundaries_Full_Clipped_EW_BFC_2022_-6437031168783062454.gpkg')
```

```{r}
plot(st_geometry(lsoa["LSOA21NM"]),lwd=0.1)
```

```{r}
library(readxl)
dep<-read_excel("File_1_-_IMD2019_Index_of_Multiple_Deprivation.xlsx",sheet="IMD2019",col_names = TRUE)
depData<-merge(lsoa,dep,by.x="LSOA21CD",by.y="LSOA code (2011)",all.x=TRUE)
```

```{r}
depla<-read_excel("File_10_-_IoD2019_Local_Authority_District_Summaries__lower-tier__.xlsx",sheet="IMD",col_names=TRUE)
deplaData<-merge(la,depla,by.x="LAD22CD",by.y="Local Authority District code (2019)",all.x=TRUE)
deplaData1<-merge(deplaData,data.frame(clustercount)[,1:2],by="LAD22NM")
```

```{r}
mandep<-depData[grepl("Manchester", depData$LSOA21NM), ]
bmhdep<-depData[grepl("Birmingham", depData$LSOA21NM), ]

```

```{r}
eps<-100
minPts<-3
coord<-st_coordinates(joined$`_ogr_geometry_`)
nn<-frNN(coord,eps) #eps
test<-dbscan(nn,minPts=minPts) #minPoint
labels<-test$cluster
cat(paste("When eps =",eps),"and",paste("minPts =",minPts),", the   number of labels is:")
print(max(labels))
testData<-joined
testData$label<-labels
testData$layer<-testData$label%%26 
testData$layer<-as.factor(testData$layer)

core<-is.corepoint(coord,eps,minPts=minPts)
circle<-st_buffer(testData[core,],eps)
cl_boundary<-circle %>% group_by(label) %>% summarise(`_ogr_geometry_`=st_union(`_ogr_geometry_`),do_union=FALSE)
```


```{r}
labelmap = tm_shape(bmhdep) +tm_polygons(col="Index of Multiple Deprivation (IMD) Decile",id="Index of Multiple Deprivation (IMD) Decile") + 
  tm_shape(testData) + tm_dots(legend.show = FALSE, col="layer",id="label",palette=paletteer_d("ggsci::default_ucscgb")) + tm_shape(cl_boundary) +tm_borders() + tmap_options(check.and.fix = TRUE) 

```

```{r}
lalabelmap = tm_shape(engdepladata) +tm_polygons(col="IMD - Rank of average rank") #+ tm_shape(engdepladata1) + tm_symbols(col="red",size="clusters") 
laclumap = tm_shape(engdepladata1) + tm_polygons(col="clusters") 
```

```{r}
tmap_mode("plot")
lalabelmap
laclumap
```
```{r}
tmap_save(lalabelmap,"IMD.pdf")
tmap_save(laclumap,"ClusterEng.pdf")
```


```{r}
tmap_mode("view")
labelmap
```

```{r}
tmap_save(labelmap,"labelmap.html")
```

deprivation analysis at lsoa level
```{r}
newtest<-st_join(testData,depData,join=st_within)
```

```{r}
noth<-newtest[is.na(newtest$LSOA21CD),]
```


```{r}
testNull<-newtest[is.na(newtest$LSOA21CD),]
#joinNull<-joined[is.na(joined$LAD22CD),]
tmap_mode("view")
Null = #tm_shape(st_geometry(uk), col = "gray", lwd = 1,name="UK") + tm_polygons() + 
  #tm_layout(frame = FALSE) + tm_shape(la["LAD22NM"],id="LAD22NM",name="WLocal Authority") + tm_polygons() +
  #tm_shape(st_geometry(wards["WD22NM"]),lwd=0.05,name="Wards") + tm_polygons(id="WD22NM") + 
  #tm_shape(joinNull) + tm_dots(legend.show = TRUE,col="amenity", id="name")
  tm_shape(testNull) + tm_dots(legend.show = TRUE,col="amenity", id="label")
Null
```

```{r}
engnewtest<-newtest[grepl("E", newtest$LAD22CD), ]
resul <- newtest %>%
  group_by(`Index of Multiple Deprivation (IMD) Decile`) %>%
  summarise(clusters = n_distinct(label)-1)

```

for loops
```{r}
for (eps in c(50,100,150,200,250,300)) {
  for (minPts in c(2,3,5)) {
    coord<-st_coordinates(joined$`_ogr_geometry_`)
    nn<-frNN(coord,eps) #eps
    test<-dbscan(nn,minPts=minPts) #minPoint
    labels<-test$cluster
    cat(paste("When eps =",eps),"and",paste("minPts =",minPts),", the   number of labels is:")
    print(max(labels))
    testData<-joined
    testData$label<-labels
    testData$layer<-testData$label%%26 
    testData$layer<-as.factor(testData$layer)
    
    newtest<-st_join(testData,depData,join=st_within)
    result <- newtest %>%
  group_by(`Index of Multiple Deprivation (IMD) Decile`) %>%
  summarise(clusters = n_distinct(label)-1)
    table<-as.data.frame(result)
    filename3<-paste0("eps_",eps,"_minPts_",minPts,".csv")
    write_csv(table[,1:2],filename3)
  }
}
```

## Parallel running
```{r}
library(parallel)
```

```{r}
# 设定使用的核心数并创建一个cluster
cores <- detectCores()
cl <- makeCluster(4)


clusterExport(cl, "joined")
# 使用parLapply并行计算
results <- parLapply(cl, unique(testData$LAD22NM), function(x) {
  library(sf)
  library(dbscan)
  library(dplyr)
  eps<-100
  minPts<-3
  coord<-st_coordinates(joined$`_ogr_geometry_`)
  nn<-frNN(coord,eps) #eps
  test<-dbscan(nn,minPts=minPts) #minPoint
  labels<-test$cluster
  cat(paste("When eps =",eps),"and",paste("minPts =",minPts),", the   number of labels is:")
  print(max(labels))
  testData<-joined
  testData$label<-labels
  
  core<-is.corepoint(coord,eps,minPts=minPts)
  circle<-st_buffer(testData[core,],eps)
  cl_boundary<-circle %>% group_by(label) %>% summarise(`_ogr_geometry_`=st_union(`_ogr_geometry_`),do_union=FALSE)
  
  Data<-testData[testData$LAD22NM==x,]
  # manCluNumIn<-st_within(cl_boundary,la[la$LAD22NM=="Manchester",])
  # manClu<-which(as.vector(as.matrix(manCluNumIn))) 
  Clu<-unique(Data$label)
  Clu<-Clu[Clu!=0]
  #find out the num of cluster contained in Manchester
  filename2<-paste0(x,"_eps_",eps,"_minPts_",minPts,".txt")
  con<-file(filename2,"w")
  writeLines(paste("The number of clusters in", x,"with epsilon",eps,"and minimum points", minPts, ":", length(Clu)), con)
  for (cluster in Clu){
    data<-testData[testData$label==cluster,]
    writeLines(paste("cluster number:",cluster),con)
    writeLines(paste(names(table(data$amenity)), table(data$amenity)), con)
  }
  close(con)
  
   # Clean up unnecessary variables after each loop
  rm(coord, nn, test, labels, testData, core, circle, cl_boundary, labelmap, manData, Clu, data, filename, filename2, con)
  gc()  # manually call the garbage collector
})

# 停止cluster
stopCluster(cl)

```


## AHAH
```{r}
ahah<-read.table("ahahv2domainsindex.csv",sep=",",header=TRUE)
ahahData<-merge(lsoa,ahah,by.x="LSOA21CD",by.y="lsoa11",all.x=TRUE)
```

```{r}
manahah<-ahahData[grepl("Manchester", ahahData$LSOA21NM), ]
```

```{r}
ahahtest<-st_join(testData,ahahData,join=st_within)
```

```{r}
ahahmap = tm_shape(manahah) +tm_polygons(col="d_ahah",id="d_ahah",title = "AHAH - Decile") + tm_shape(testData[grepl("Manchester", testData$LAD22NM), ]) + tm_dots(legend.show = FALSE, col="layer",id="label",palette=paletteer_d("ggsci::default_ucscgb")) + tm_shape(cl_boundary) +tm_borders() + tmap_options(check.and.fix = TRUE) 
tmap_mode("plot")
ahahmap
```
```{r}
tmap_save(ahahmap,"ahahmap.pdf")
```

```{r}
engahahtest<-ahahtest[grepl("E", ahahtest$LAD22CD), ]
resultahah <- engahahtest %>%
  group_by(d_ahah) %>%
  summarise(clusters = n_distinct(label)-1)

```

```{r}
resultahah <- ahahtest %>%
  group_by(d_ahah) %>%
  summarise(clusters = n_distinct(label)-1)
```
